Section_8_Team1_Lab2_Report

### 2021-08-04 reports/Draft_Report.Rmd
EDA and models added to report

#we may not need all of these
library(tidyverse)
library(magrittr)
library(ggplot2)
library(patchwork)
library(sandwich)
library(lmtest)
library(dplyr)
library(table1)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = TRUE)

@@

#### Operationalization of focus variables
We gathered covid case and death data from NYT. We gathered trip distance data from the Bureau of Transportation, which they record based on data gathered from personal mobile devices. This data was presented as number of travelers in binned distances. We defined a short trip as less than 100 miles and long trips as greater than 100 miles. This was decided under the assumption that distances traveled of less than 100 miles are for the purpose of commuting, while greater than 100 miles indicated vacation travel.

#### Operationalization of additional variables
To enrich our model and limit OVB, we brainstormed a number of additional variables that could affect travel rates during covid. For one, we looked at location due to the assumption that those who live in rural settings are likely to commute farther than those in an urban setting. We also looked at age, gender, income demographics. Finally, we pulled in data for county population to normalize all the data on a per capita basis.

@@

```{r dataframe, echo=FALSE}
df <- read.csv('/home/jovyan/r_bridge/code/lab-2-lab2_section8_jal/data/interim/covid_trips_interim.csv')
head(df)

@@

To demonstrate the operationalization of the data, Tables 1 and 2 below display the original value counts from the dataset as well as how many values were removed as a part of filtering the dataset to remove all states except Texas. For the analysis, $$### responses were analyzed as shown in Table 1. Table 2 depicts the county type breakdown for rural or urban classification as well.

@@

#probably going to have to transform total_pop

ggplot(df, aes(x=total_pop)) + geom_histogram(bins=100))
ggplot(df, aes(x=sum_cases)) + geom_histogram(bins=100)
ggplot(df, aes(x=sum_deaths)) + geom_histogram(bins=100) 
ggplot(df, aes(x=long_trip)) + geom_histogram(bins=100)

@@

#need to change these to per capita data
model1 <- lm(long_trip ~ cases + deaths, data = df) #limited model
model2 <- lm(, data = )
model3 <- lm(, data = ) #final model

@@

#Run coeftest to show statistical significanve of all variables in the model
coeftest(model3, vcov = vcovHC(model3, type="HC1"))
```

@@

#run this to display the CLM graphs needed to verify CLM assumptions met
#par(mfrow = c(2, 2))
#plot(model2)

##FINAL MODEL
#par(mfrow = c(2, 2))
#plot(model3)

>>>>

#we may not need all of these
library(tidyverse)
library(magrittr)
library(ggplot2)
library(patchwork)
library(sandwich)
library(lmtest)
library(dplyr)
library(table1)
library(ggally)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = TRUE)

@@

#### Operationalization of focus variables
We gathered covid case and death data from NYT. We gathered trip distance data from the Bureau of Transportation, which they record based on data gathered from personal mobile devices. This data was presented as number of travelers in binned distances. We defined a short trip as less than 100 miles and long trips as greater than 100 miles. This was decided under the assumption that distances traveled of less than 100 miles are for the purpose of commuting, while greater than 100 miles indicated vacation travel. Hand in hand with this variable is our indicator variable for urban vs rural setting *** how did we decide this again, population threshold?**** under the assumption that those who live in rural settings are likely to commute further than those in an urban setting. Finally, we believe that median household income plays a significant role in an individual's ability to take vacations. We pulled this directly from the US Census Bureau.

#### Operationalization of additional variables
To enrich our model and limit OVB, we brainstormed a number of additional variables that could affect travel rates during covid. For one, we looked at how covid affected the county, through the unemployment rate. We also looked at age, gender, income demographics. Then, in addition to income demographics, we focused on percent of younger folks, as defined as those younger than 17 and older folks as defined as those older than 65 because of the nature of how covid affects an individual.

@@

```{r dataframe, echo=FALSE}
df <- read.csv('/home/jovyan/r_bridge/code/lab-2-lab2_section8_jal/data/interim/covid_trips_interim_model3.csv')
head(df)

@@

To demonstrate the operationalization of the data, Tables 1 and 2 below display the original value counts from the dataset as well as how many values were removed as a part of filtering the dataset to remove all states except Texas. For the analysis, ### responses were analyzed as shown in Table 1. Table 2 depicts the county type breakdown for rural or urban classification as well.

@@

#Short vs long trip: rate of short trips is higher than rate of long trips in relation to # of covid cases
ggplot(data = df) + aes(x = log(sum_cases), y = log(long_trip)) + geom_point()

ggplot(data = df) + aes(x = log(sum_cases), y = log(short_trip)) + geom_point()

df %>% 
  mutate(
    total_pop = log(total_pop),
    cases = log(cases+1),
    deaths = log(deaths+1),
    long_trip = log(long_trip),
    density = log(density)
  ) %>%
  select(long_trip, cases, deaths, median_income, unempoy_rate, density, pct_lt17) %>% 
  GGally::ggpairs(.,
               legend = 1,
               mapping = ggplot2::aes(colour=as.factor(df$is_rural)))

@@

#need to change these to per capita data
model1 <- lm(log(long_trip+1) ~ log(cases+1) + log(deaths+1) + is_rural + median_income, data = df) #limited model
model2 <- lm(log(long_trip+1) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density), data = df)
model3 <- lm(log(long_trip+1) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density) + pct_lt17, data = df) #final model

@@

#Run coeftest to show statistical significance of all variables in the model
coeftest(model3, vcov = vcovHC(model3, type="HC1"))
```

@@

#run this to display the CLM graphs needed to verify CLM assumptions met
par(mfrow = c(2, 2))
plot(model2)

##FINAL MODEL
par(mfrow = c(2, 2))
plot(model3)
